### 2018-06-25 Thesis/Parts/Abstract/Abstract.tex
thesis, version 1.0

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\fakeheader{Abstract}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on, or in combination with, generic texts, which are not limited the characteristics of in-domain texts, such as rare domain specific words. This research focusses on the usefulness of word embeddings on domain specific texts, concerning 1.391.543 scientific articles which have been published in 2017.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\fakeheader{Abstract}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused generic texts, which are not limited the characteristics of in-domain texts such as rare domain specific words, or have focussed on small sets academic texts. This research focusses on the usefulness of word embeddings on domain specific texts, concerning 1.391.543 scientific articles which have been published in 2017.
\end{document}
